Variation in Economic Growth From Civil Conflict

### 2015-04-25 LaTeX/Presentation/PreezeText.tex
r and r letter

\begin{itemize}
\item Krugman 1991; Henderson 2000; Hanson 2005 - Cities are important drivers of economic growth
\item Heterogeneity in effect of conflict on growth is due to spatial proximity of conflict relative to major urban centers
\end{itemize}

@@

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\begin{itemize}
	\item Collier (1999) - destruction, disruption, diversion, dissaving, portfolio substitution
	\item Imai \& Weinstein (2005) - geographical spread of conflict
	\end{itemize}
	\item Economic Performance $\rightarrow$ Civil War
	\begin{itemize}
	\item Collier et al. (2003) - the conflict trap
	\item Fearon \& Laitin (2003) - poor economic growth conducive for civil war
	\end{itemize}
	\item Disaggregating Civil Wars
	\begin{itemize}
	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item Cities $\rightarrow$ Growth
	\begin{itemize}
	\item Marshall (1920) - geographic clustering promotes valuable learning and exchange between actors
	\item Lucas (1998) \& Glaeser et al. (1992) - accumulation of human capital generates positive spillovers
	\item Venables (2005) - economy consists of ``lumps'' of productivity and swaths of areas contributing little to growth	
	\end{itemize}
	\item Cities \& Conflict $\rightarrow$ Growth
	\begin{itemize}
	\item Conflicts have heterogeneous effects on economic growth 
	\item Effects determined by spatial proximity to economically relevant centers such as cities
	\end{itemize}
\end{itemize}

@@

\begin{block}{Conclusions}
\begin{itemize}
	\item Novel approach in the study of civil conflict to distinguish between spatially dissimilar events
	\item Proximity of conflict to major cities explains disparate economic outcomes
\end{itemize}
\end{block}

\begin{block}{Next Steps}
\begin{itemize}
\item Account for other economically important locations (e.g., oil fields)
\item Alternative methods to address aggregation problem
\item More refined analysis within a country using subnational economic data
\end{itemize}
\end{block}

>>>>

\pause
\begin{itemize}
\item Krugman 1991; Henderson 2000; Hanson 2005 - Cities are important drivers of economic growth
\pause
\item Heterogeneity in effect of conflict on growth is due to spatial proximity of conflict relative to major urban centers
\end{itemize}

@@

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\begin{itemize}
	\item Collier (1999) - destruction, disruption, diversion, dissaving, portfolio substitution
	% \item Imai \& Weinstein (2005) - geographical spread of conflict
	\end{itemize}
	\pause
	\item Economic Performance $\rightarrow$ Civil War
	\begin{itemize}
	% \item Collier et al. (2003) - the conflict trap
	\item Fearon \& Laitin (2003) - poor economic growth conducive for civil war
	\end{itemize}
	\pause
	\item Disaggregating Civil Wars
	\begin{itemize}
	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item Cities $\rightarrow$ Growth
	\begin{itemize}
	\item Marshall (1920) - geographic clustering promotes valuable learning and exchange between actors
	\pause
	\item Lucas (1998) \& Glaeser et al. (1992) - accumulation of human capital generates positive spillovers
	\pause
	\item Venables (2005) - economy consists of ``lumps'' of productivity and swaths of areas contributing little to growth	
	\end{itemize}
	\pause
	\item Cities \& Conflict $\rightarrow$ Growth
	\begin{itemize}
	\item Conflicts have heterogeneous effects on economic growth 
	\item Effects determined by spatial proximity to economically relevant centers such as cities
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Account for other economically important locations (e.g., oil fields, highways connecting cities)
\item More refined analysis within a country using subnational economic data
\end{itemize}
